Implementing Real-Time Transport Services over an Ossified Network

### 2016-06-22 paper.tex
Address review 2A comment about in-network state

\textbf{Connection and Congestion Control:}
We note the importance of congestion control. %Clearly,
Historically real-time applications needed an isochronous channel,
and needed to avoid subjected to congestion control. This is impractical on the
Internet. Further, while some applications are non-adaptive or constant bitrate,
an increasing number are either or both of adaptive and variable bitrate.
Users would be better served by applications that adapt to available bandwidth.

We note that a connection-oriented transport is a lesser, but useful,
requirement.
% for many real-time multimedia applications.
Indeed, flexibility to
change the destination within a call is beneficial for
applications that support mobile users, or for some forms of multiparty session.
However, to support NAT traversal and to help dynamically manage firewall
pinholes, it is often desirable, though not necessary, for the transport to be connection oriented. We
believe these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. Similarly, while not strictly
needed by the applications, it is beneficial if the transport provides a
keep-alive service to refresh NAT and firewall bindings if the application goes
silent.

>>>>

\textbf{Connections and Congestion Control:}
We note the importance of congestion control. Historically, real-time many
applications have required an isochronous channel, that is not subject to
congestion control. This is impractical on the Internet. Further, while
some applications are non-adaptive or constant bit-rate, an increasing
number are either or both of adaptive and variable bit-rate. Users would
be better served by applications that adapt to available bandwidth.

We note that a connection-oriented transport is a lesser requirement for
many real-time multimedia applications. 
Indeed, flexibility to change the destination within a call is beneficial
for applications that support mobile users, and for some forms of multiparty
session.
Maintaining per-connection state at the endpoints is helpful for the
implementation of many forms of congestion control, however. 
Signalling messages indicating start and end of connections can also ease
NAT traversal, and help dynamically manage firewall pinholes, by indicating
when in-network state should be created and can be torn down. 
Accordingly, it is often desirable for the transport to be connection
oriented.

We believe these concerns outweigh the benefits of connectionless transport, and so
add a requirement for connection oriented service. Similarly, while not strictly
needed by the applications, it is beneficial if the transport provides a
keep-alive service to refresh NAT and firewall bindings if the application goes
silent.
